Asymmetric continuous prediction bands for assessing the validity of smooth biomechanical curve data

### 2021-08-27 paper.Rmd
Change windows to unix path in Rmd
Correctly implement coverage for single curve cross validation´

dir.script <- "C:/Users/Daniel/Desktop/tmp/floa/R"
dir.data <- "C:/Users/Daniel/Desktop/tmp/floa/R/examples"

source(paste0(dir.script, "/example_data.R"))
source(paste0(dir.script, "/pick_subwise_curves.R"))
source(paste0(dir.script, "/draw_clusters.R"))
source(paste0(dir.script, "/functional_mean.R"))
source(paste0(dir.script, "/functional_sd.R"))
source(paste0(dir.script, "/boot_mean_sd.R"))
source(paste0(dir.script, "/floa_rcb.R"))
source(paste0(dir.script, "/floa_point.R"))
source(paste0(dir.script, "/floa_roislien.R"))
source(paste0(dir.script, "/plot_loa.R"))
source(paste0(dir.script, "/get_coverage.R"))
source(paste0(dir.script, "/get_coverage_fraction.R"))
source(paste0(dir.script, "/crossval_coverage.R"))
source(paste0(dir.script, "/crossval_coverage_fraction.R"))
source(paste0(dir.script, "/plot_cov_ver.R"))
```

@@

<!-- Aus Robinson et al. (2021) -->
<!-- Exemplar 1D eects from the biomechanics literature across a range of signal types were collated and reported (Bakke & Besier, 2020, Barrios & Willson, 2017, Bovi, Rabuetti, Mazzoleni, & Ferrarin, 2011, Phan et al., 2017, Gomes, Ackermann, Ferreira, Orselli, & Sacco, 2017, Robinson et al., 2014). -->

<!-- the code to reproduce all 1D eects is provided at https://github.com/m-a-robinson/sample-size -->

@@

### Leave-one-out cross validation

@@

* 5. FLoA~Point~ : Pointwise B & A Limits of Agreement

@@

* a: Percentage of entirely covered curves (all points within the limits): Each box consists of n~ = 11 values (one percentage for each subject).

@@

```{r warning = FALSE, message = FALSE, eval = FALSE}
lwr.bnd <- floa["lower", ]
upr.bnd <- floa["upper", ]

# ...

for (stride.idx in stride.indices){
    curve <- subset(device.diff, strideID == stride.idx)

@@

    # Check if the entire curve is within the limits
    if (points.outside > 0) {
      outside <- outside + 1
    }
  }

coverage <- 1 - (outside / n.strides)
```

cover.cross <- crossval_coverage(data, n.boot)
# colnames(cover.cross) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")

plot_cov_ver(cover.cross)

# knitr::kable(cover.cross, caption = "Percentages (entire curve covered) for every leave one out fold")
```

```{r warning = FALSE, message = FALSE, eval = FALSE}
lwr.bnd <- floa["lower", ]
upr.bnd <- floa["upper", ]

# ...

for (stride.idx in stride.indices){

  curve <- subset(device.diff, strideID == stride.idx)

  # Mean percentage of points outside the limits
  inside <- below.thresh == above.thresh
  inside.thresh.perc <- c(inside.thresh.perc,
                          mean(sum(inside[TRUE]) / length(curve$value)))
}
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Display cross validation coverages (mean fraction of the curve that is covered) across methods
cover.cross.fraction <- crossval_coverage_fraction(data, n.boot)

plot_cov_ver(cover.cross.fraction)
```

@@

cover.cross <- crossval_coverage(data, n.boot)
# colnames(cover.cross) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")

plot_cov_ver(cover.cross)

# knitr::kable(cover.cross, caption = "Percentages (entire curve covered) for every leave one out fold")
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Display cross validation coverages (fraction of the curve that is covered) across methods
cover.cross.fraction <- crossval_coverage_fraction(data, n.boot)

plot_cov_ver(cover.cross.fraction)
```

>>>>

dir.script <- "~/floa/R"
dir.data <- "~/floa/R/examples"

source(paste0(dir.script, "/example_data.R"))
source(paste0(dir.script, "/pick_subwise_curves.R"))
source(paste0(dir.script, "/draw_clusters.R"))
source(paste0(dir.script, "/functional_mean.R"))
source(paste0(dir.script, "/functional_sd.R"))
source(paste0(dir.script, "/boot_mean_sd.R"))
source(paste0(dir.script, "/floa_rcb.R"))
source(paste0(dir.script, "/floa_point.R"))
source(paste0(dir.script, "/floa_roislien.R"))
source(paste0(dir.script, "/plot_loa.R"))
source(paste0(dir.script, "/get_coverage.R"))
source(paste0(dir.script, "/get_coverage_singlecurve.R"))
source(paste0(dir.script, "/get_coverage_fraction.R"))
source(paste0(dir.script, "/get_coverage_singlecurve_fraction.R"))
source(paste0(dir.script, "/crossval_coverage.R"))
source(paste0(dir.script, "/singlecurve_coverage.R"))
source(paste0(dir.script, "/crossval_coverage_fraction.R"))
source(paste0(dir.script, "/singlecurve_coverage_fraction.R"))
source(paste0(dir.script, "/plot_cov_ver.R"))
```

@@

<!-- Aus Robinson et al. (2021) -->
<!-- Exemplar 1D effects from the biomechanics literature across a range of signal types were collated and reported (Bakke & Besier, 2020, Barrios & Willson, 2017, Bovi, Rabuetti, Mazzoleni, & Ferrarin, 2011, Phan et al., 2017, Gomes, Ackermann, Ferreira, Orselli, & Sacco, 2017, Robinson et al., 2014). -->

<!-- the code to reproduce all 1D effects is provided at https://github.com/m-a-robinson/sample-size -->

@@

### Leave-one (curve) out cross validation

@@

* 5. FLoA~Point~ : Pointwise B & A Limits of Agreement (SD derived from linear mixed effects model)

@@

* a: Percentage of entirely covered curves (all points within the limits)

@@

```{r warning = FALSE, message = FALSE, eval = FALSE}
get_coverage_singlecurve <- function (curve, floa) {
  # Curve is a numerical vector
  # floa is a "matrix" "array" containing "lower" and "upper" limits

  # Calculate coverage (entire curves within the percentile boundaries)
  # ----------------------------------------------------------------------------
  lwr.bnd <- floa["lower", ]
  upr.bnd <- floa["upper", ]

  outside <- 0

  # Compare curves with upper and lower boundaries
  below.thresh <- curve < lwr.bnd
  above.thresh <- curve > upr.bnd

  coverage <- ifelse(points.outside > 0, 0, 1)

  return(coverage)
}
```

# Leave-one curve out approach
# ------------------------------------------------------------------------------
cover.cross.singlecurve <- singlecurve_coverage(data, n.boot)

# Calculate percent from counts
calculate_percent <- function(data) {
  percentage <- (sum(data) / length(data))
  percentage <- round(percentage, digits = 2)
}

covered.curves.percent <- apply(cover.cross.singlecurve, 2, calculate_percent)
covered.curves.percent <- data.frame(t(covered.curves.percent))
colnames(covered.curves.percent) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")

knitr::kable(covered.curves.percent, caption = "Percentages of entire covered curves")

# # Leave-one subject out approach
# # ------------------------------------------------------------------------------
# cover.cross <- crossval_coverage(data, n.boot)
# # colnames(cover.cross) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")
# 
# plot_cov_ver(cover.cross)
```

```{r warning = FALSE, message = FALSE, eval = FALSE}
get_coverage_singlecurve_fraction <- function (curve, floa) {
  # Curve is a numerical vector
  # floa is a "matrix" "array" containing "lower" and "upper" limits

  # Calculate coverage (curve points within the percentile boundaries)
  # ----------------------------------------------------------------------------
  lwr.bnd <- floa["lower", ]
  upr.bnd <- floa["upper", ]

  outside <- 0

@@

  # Divide by 101 to adjust for 101 data points
  coverage <- 1 - (points.outside / 101)
  coverage <- round(coverage, digits = 2)

  return(coverage)
}
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Leave-one curve out approach
# ------------------------------------------------------------------------------
cover.cross.fraction.singlecurve <- singlecurve_coverage_fraction(data, n.boot)
plot_cov_ver(cover.cross.fraction.singlecurve)

# # Leave-one subject out approach
# # ------------------------------------------------------------------------------
# cover.cross.fraction <- crossval_coverage_fraction(data, n.boot)
# plot_cov_ver(cover.cross.fraction)
```

@@

# Leave-one curve out approach
# ------------------------------------------------------------------------------
cover.cross.singlecurve <- singlecurve_coverage(data, n.boot)

# Calculate percent from counts
calculate_percent <- function(data) {
  percentage <- (sum(data) / length(data))
  percentage <- round(percentage, digits = 2)
}

covered.curves.percent <- apply(cover.cross.singlecurve, 2, calculate_percent)
covered.curves.percent <- data.frame(t(covered.curves.percent))
colnames(covered.curves.percent) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")

knitr::kable(covered.curves.percent, caption = "Percentages of entire covered curves")

# # Leave-one subject out approach
# # ------------------------------------------------------------------------------
# cover.cross <- crossval_coverage(data, n.boot)
# # colnames(cover.cross) <- c("RCB_1", "RCB_2", "RCB_3", "Roislien_4", "Point_5")
# 
# plot_cov_ver(cover.cross)
```

@@

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Leave-one curve out approach
# ------------------------------------------------------------------------------
cover.cross.fraction.singlecurve <- singlecurve_coverage_fraction(data, n.boot)
plot_cov_ver(cover.cross.fraction.singlecurve)

# # Leave-one subject out approach
# # ------------------------------------------------------------------------------
# cover.cross.fraction <- crossval_coverage_fraction(data, n.boot)
# plot_cov_ver(cover.cross.fraction)
```
